---
title: "Formative Assessment 6"
author: "Vera Aguila"
date: "2024-02-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I. **Geometric Distribution.** Provide an R code for the geometric distribution. The geometric distribution is a probability distribution that models the number of trials required to achieve the first success in a sequence of Bernoulli trials, where each trial has a constant probability of success.

1. Set the probability of success:  p <- 0.2

```{r gd1}
 p <- 0.2
```

2. Generate 1000 random variables from the geometric distribution.

```{r gd2}
 n <- 1000 
 k <- rgeom(n, p)
```

3. Calculate some basic statistics:

mean_x <- mean(x)

var_x <- var(x)

sd_x <- sd(x)

```{r gd3}
 tofirstsuccess <- k+1
 mean_x <- mean(tofirstsuccess)
 var_x <- var(tofirstsuccess)
 sd_x <- sd(tofirstsuccess)
```

4. Print the results in item 3 with the following output (string):

Number of trials required to achieve first success:

Mean (in 2 decimal places):

Variance (in 2 decimal places):

Standard deviation ( in 2 decimal places):

```{r gd4, echo=FALSE}
 cat("Number of trials required to achieve first success:",k,"\n")
 cat("Mean (in 2 decimal places): ", sprintf("%.2f", mean_x), "\n", sep="")
 cat("Variance (in 2 decimal places): ", sprintf("%.2f", var_x), "\n", sep="")
 cat("Standard deviation ( in 2 decimal places): ", sprintf("%.2f", sd_x), "\n", sep="")
```

5. Plot the histogram of the results.

The red line represents the mean.

```{r gd5}
hist(k, breaks = 20, col = "#f29b9b", main = "Histogram of Geometric Distribution", xlab = "Number of Trials", ylab = "Frequency")
abline(v = mean_x, col='red', lwd = 3)
```



II. **Hypergeometric Distribution.**  Consider a plant manufacturing IC chips of which 10% are expected to be defective. The chips are packed in boxes for export. Before transportation, a sample is drawn from each box. Estimate the probability that the sample contains more than 10% defectives, when:

proportion of successes = p = 0.10

1. A sample of 10 is selected from a box of 40;

total number = N = 40
<br>number chosen = n = 10
```{r hgd1}
x <- 2:4
k <- dhyper(x, 4, 36, 10)
k
sum(k)
plot(x, dhyper(x, 4, 36, 10),
xlab = "Number of defective", type = "h",
ylab = "P(X = x)",
main = "N = 40, M = 4, n = 10", font.main = 1)
phyper(4, 4, 36, 10)

plot(x, phyper(x, 4, 36, 10),
xlab = "Number of defective", type = "s",
ylab = "P(X <= x)",
main = "N = 40, M = 4, n = 10", font.main =1)

```

2. A sample of 10 is selected from a box of 5000.

total number = N = 5000
<br>number chosen = n = 10

```{r hgd2}

p <- 0.1
N = 5000
n = 10
def_n = N*p
x <- 2:n
k <- dhyper(x, def_n, N-def_n, n)
k
sum(k)

plot(x, k,
xlab = "Number of defective", type = "h",
ylab = "P(X = x)",
main = "N = 5000, M = 4500, n = 10", font.main = 1)
phyper(4, 4, 36, 10)

plot(x, phyper(x, def_n, N-def_n, n),
xlab = "Number of defective", type = "s",
ylab = "P(X <= x)",
main = "N = 5000, M = 500, n = 10", font.main =1)

```